---
title: "crab practice"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

```{r}
library(lterdatasampler)
library(tidyverse)
library(kableExtra)
```

## Introduction Statement

The below graph and table were created to show the relationships between water temperature and latitude, and the corresponding changes in Atlantic marsh fiddler crab, *Minuca pugnax* carapace size across sites.

```{r}
#| fig-cap: "this is my caption"
ggplot(data = pie_crab, aes(y = latitude, x = water_temp)) +
  geom_point() + 
  labs(x= "Water Temperature (C)",
       y = "Latitude")
```

```{r}
crab_stats <- pie_crab %>% group_by(latitude, site) %>% 
  summarise(
  n = n(), 
  mean_mm = mean(size),
  min_mm = min(size),
  max_mm = max(size),
  sd_mm = sd(size),
  median_mm = median(size)
  ) 

crab_stats |>
  kable(col.names = c("Latitude", "Site", "Count", "Mean Carapace Length (mm)", "Minimum Carapace Length (mm)", "Max Carapace Length (mm)", "Length Standard Deviation (mm)", "Length Median (mm)"))
  
citation("lterdatasampler")
```

## Citations

-   Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative. https://doi.org/10.6073/pasta/4c27d2e778d3325d3830a5142e3839bb (Accessed 2021-05-27).
-   Johnson DS, Crowley C, Longmire K, Nelson J, Williams B, Wittyngham S. The fiddler crab, Minuca pugnax, follows Bergmann’s rule. Ecol Evol. 2019;00:1–9. https://doi.org/10.1002/ece3.5883
